---
title: "Can k-mean clustering evaluates psychological questionnaires better than human? "
author: "Melina Mazloum, Ali Rahjouei"
date: "8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading libraries
```{r LoadingLibraries, echo=F}
library(tidyverse)
library(xlsx)
library(factoextra)
library(reshape)
library(corrplot)
library(apcluster)
```

Loading data
```{r LoadingData, echo=FALSE}
dataset = read.xlsx(file="/home/arahjou/Downloads/Melina Thesis/Total_form_20220814_3.xlsx", 1, header = T)
```

## Comparing scores GAD7 vs. GHQ28-Anxiety

```{r}
ggplot(dataset, aes(x=GAD7_Score, y= GHQ_28_Angst)) + 
  geom_point() + geom_smooth(method = lm)
```



## Classic

```{r}
#GAD7
library(ggplot2)
mydata = dataset %>% group_by(GAD7_Qualitative)  %>% count(GAD7_Qualitative)
mydata$GAD7_Qualitative = factor(mydata$GAD7_Qualitative, levels=c("Minimal", "Mild", "Mittelgradig", "Schwer"))
ggplot(mydata, aes(x=GAD7_Qualitative, y=n, fill=GAD7_Qualitative)) + 
  geom_col(color="black") + scale_fill_manual(values = c("#eb86dd","#2E9FDF", "#00AFBB", "#E7B800")) + theme_bw()

## GHQ28-Anxiety

mydata = dataset %>% group_by(GHQ_28_Angst_Qualitative)  %>% count(GHQ_28_Angst_Qualitative)
mydata$GHQ_28_Angst_Qualitative = factor(mydata$GHQ_28_Angst_Qualitative, levels=c("Unauffällig", "Mittelgradig", "Schwer"))
ggplot(mydata, aes(x=GHQ_28_Angst_Qualitative, y=n, fill=GHQ_28_Angst_Qualitative)) + 
  geom_col(color="black") + scale_fill_manual(values = c("#eb86dd", "#00AFBB", "#E7B800")) + theme_bw()


```


## GAD7

```{r , echo=FALSE}
mydata = dataset[, c(47:53)]
rownames(mydata) = paste(dataset$ID ,dataset$GAD7_Qualitative)
for (i in 1:7){
  mydata[,i] = as.numeric(unlist(mydata[,i]))
}
scaledata = scale(mydata)
```

## Clustring questions based on scores

```{r , echo=FALSE}
hc <- hclust(as.dist(1-cor(scaledata, method="spearman")), method="complete") # Clusters columns by Spearman correlation.
TreeC = as.dendrogram(hc, method="average")
plot(TreeC,
     main = "Sample Clustering",
     ylab = "Height")

```



## Making hierarchical and heatmap

```{r, echo=F }
#make the matrix
dist <- cor(t(scaledata), method="pearson")
#make the tree
hr <- hclust(as.dist(1-dist), method="complete") # Cluster rows by Pearson correlation.
```

## Ploting all identified clusters

```{r , echo=F}
set.seed(20)
kClust <- kmeans(scaledata, centers= 4, nstart = 1000, iter.max = 100)
kClusters <- kClust$cluster

```


```{r , echo=F}
# function to find centroid in cluster i
clust.centroid = function(i, dat, clusters) {
  ind = (clusters == i)
  colMeans(dat[ind,])
}
kClustcentroids <- sapply(levels(factor(kClusters)), clust.centroid, scaledata, kClusters)
```


## Investigating clusters correlation

```{r, echo=FALSE }
corralation <- cor(kClustcentroids)
corrplot(corralation, method="circle")
corrplot(corralation, method="number")
```

## Visulaizing clusters

```{r, echo=F}
set.seed(123)
res.km <- kmeans(scale(mydata), 4, nstart = 25)
# K-means clusters showing the group of each individuals
res.km$cluster


fviz_cluster(res.km, data = mydata,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#eb86dd"), 
             geom = c("point", "text"),
             ellipse.type = "convex", 
             ggtheme = theme_bw()
             )
```


```{r}
result = factor(unname(res.km$cluster))

result = summary(result)
result = c(5, 11, 19, 25)

names(result) = (c("Minimal", "Mild", "Mittelgradig", "schwer"))

barplot((result), col= c("#eb86dd","#2E9FDF", "#00AFBB", "#E7B800"))

```



## GHQ28-Anxiety

```{r , echo=FALSE}
mydata = dataset[, c(93:99)]

rownames(mydata) = paste(dataset$ID, dataset$GHQ_28_Angst_Qualitative)

for (i in 1:7){
  mydata[,i] = as.numeric(unlist(mydata[,i]))
}

scaledata = scale(mydata)
```


## Clustring questions based on scores

```{r , echo=FALSE}
hc <- hclust(as.dist(1-cor(scaledata, method="spearman")), method="complete") # Clusters columns by Spearman correlation.
TreeC = as.dendrogram(hc, method="average")
plot(TreeC,
     main = "Sample Clustering",
     ylab = "Height")

```


## Ploting all identified clusters

```{r , echo=F}
set.seed(20)
kClust <- kmeans(scaledata, centers= 4, nstart = 1000, iter.max = 100)
kClusters <- kClust$cluster

```


## Investigating clusters correlation

```{r, echo=FALSE }
corralation <- cor(kClustcentroids)
corrplot(corralation, method="circle")
corrplot(corralation, method="number")
```

## Visulaizing clusters based on test recommendation

```{r, echo=F}
set.seed(123)
res.km <- kmeans(scale(mydata), 4, nstart = 25)
# K-means clusters showing the group of each individuals
res.km$cluster


fviz_cluster(res.km, data = mydata,
             palette = c("#eb86dd", "#E7B800","#00AFBB", "#2E9FDF"),
             ggtheme = theme_bw())
               
```

```{r}
result = factor(unname(res.km$cluster))

result = summary(result)

result = c(10, 13, 17, 20)
names(result) = (c("unauffällig-1","unauffällig-2", "Mittelgradig", "schwer"))

barplot(result, col=c("#eb86dd","#2E9FDF", "#00AFBB", "#E7B800"))
```
## T-SNE GAD7

```{r}
library(Rtsne)

mydata = dataset[, c(47:53)]
rownames(mydata) = paste(dataset$ID ,dataset$GAD7_Qualitative)

for (i in 1:7){
  mydata[,i] = as.numeric(unlist(mydata[,i]))
}
scaledata = scale(mydata)

my_Rtsne <- Rtsne(X = data.matrix(scaledata),
                  perplexity = floor((nrow(scaledata) - 1) / 3),
                  dims = 2, check_duplicates = FALSE)

plot(my_Rtsne$Y, main="tsne")
```

## PCA GAD7

```{r}
mydata = dataset[, c(47:53)]
rownames(mydata) = paste(dataset$ID ,dataset$GAD7_Qualitative)

for (i in 1:7){
  mydata[,i] = as.numeric(unlist(mydata[,i]))
}
scaledata = scale(mydata)

scaledata.pca <- prcomp(scaledata, center = TRUE,scale. = TRUE)

summary(scaledata.pca)

library(ggfortify)

autoplot(scaledata.pca)
```